Reasoning about a Capability Machine with Local Capabilities

### 2017-06-01 popl-2018/paper.tex
Add a todo note...
Added comment about FTLR to answer Dominique's question.

To prove Lemma~\ref{lem:correctness-f1}, it suffices to show that the start
configuration is safe (in the $\observations$ relation) for a world with a
permanent region that requires the assertion flag to be 0. By an anti-reduction
lemma, it suffices to show that the configuration is safe after some reduction
steps. We then use a general lemma for reasoning about
\texttt{\footnotesize{scall}}, by which it suffices to show that (1) the
configuration that \texttt{\footnotesize{scall}} will jump to is safe and (2)
that the configuration just after \texttt{\footnotesize{scall}} is done cleaning
up is safe. We use the Fundamental Theorem to reason about the unknown code, but
notice that the adversary capability is an enter capability, which the
Fundamental Theorem says nothing about.\dominique{why doesn't it?}  Luckily the enter capability becomes
$\exec$ after the jump and then the Fundamental Theorem applies.

@@

>>>>

To prove Lemma~\ref{lem:correctness-f1}, it suffices to show that the start
configuration is safe (in the $\observations$ relation) for a world with a
permanent region that requires the assertion flag to be 0. By an anti-reduction
lemma, it suffices to show that the configuration is safe after some reduction
steps. We then use a general lemma for reasoning about
\texttt{\footnotesize{scall}}, by which it suffices to show that (1) the
configuration that \texttt{\footnotesize{scall}} will jump to is safe and (2)
that the configuration just after \texttt{\footnotesize{scall}} is done cleaning
up is safe. We use the Fundamental Theorem to reason about the unknown code, but
notice that the adversary capability is an enter capability, which the
Fundamental Theorem says nothing about.\dominique{why doesn't it?} \lau{The FTLR says nothing about enter capabilities, because an enter capability cannot directly be used as a program counter. The reason being that the copmutation would fail immediately and the condition in the observation relation would immediately be true (as it requires the computation to terminate and not fail). It would be trivial to show that the enter capability, data and other capabilities without execute permission is in the expression relation.}  Luckily the enter capability becomes
$\exec$ after the jump and then the Fundamental Theorem applies.

@@

\dominique{Should we also discuss the fact that we only have a semantic model
  but not a logic?}
